---
title: "607_assignment_7"
author: "Eddie Xu"
date: "2023-03-10"
output: html_document
---

The purpose of this assignment is to understand multiple file sources and its format and the structure loaded in R.

## Load Packages
```{r}
library(tidyverse)
library(xml2)
library(rvest)
library(jsonlite)
```
## Setting up multiple data sources in different formats
```{r}
xml_url <- "https://raw.githubusercontent.com/eddiexunyc/607_assignment_7/main/Resources/fav_book.xml"
json_url <- "https://raw.githubusercontent.com/eddiexunyc/607_assignment_7/main/Resources/fav_book.json"
html_url <- "https://raw.githubusercontent.com/eddiexunyc/607_assignment_7/main/Resources/fav_book.html"

```

## Load XML Dataset 
```{r}
# read xml dataset
xml_data <- read_xml(xml_url)

# read text structure in xml format
xml_structure(xml_data)
```

```{r}
# extract each data from the xml file
book_id <- xml_text(xml_find_all(xml_data, xpath = "//book_id"))
book_title <-xml_text(xml_find_all(xml_data, xpath = "//book_title"))
book_author <-xml_text(xml_find_all(xml_data, xpath = "//book_author"))
book_genre <-xml_text(xml_find_all(xml_data, xpath = "//book_genre"))
book_lang <-xml_text(xml_find_all(xml_data, xpath = "//book_lang"))
book_price <-xml_text(xml_find_all(xml_data, xpath = "//book_price"))

#convert the extracted data into a dataframe
fav_book_df <- tibble(`Book ID` = book_id , `Title` = book_title, `Author` = book_author, `Genre` = book_genre, `Language` = book_lang, `Price` = book_price)

#view the dataframe
knitr::kable(fav_book_df)
```

## Load JSON dataset
```{r}
# read JSON dataset
json_data <- fromJSON(json_url)

#convert the data into a dataframe and rename the column
json_df <- as.data.frame(json_data)
colnames(json_df) <- c("Book ID", "Title", "Author", "Genre", "Language", "Price")

#view dataframe
knitr::kable(json_df)
```

## Load HTML dataset
```{r}
# read HTML dataset
html_data <- read_html(html_url)

# convert html data into a dataframe
html_df <- html_data %>%
  html_node("table") %>%
  html_table(header = TRUE, fill = TRUE)

# view dataframe
knitr::kable(html_df)
```

## Conclusion
The data from different did not come in identical as the format structure is different between JSON, HTML, and XML. Even though the data sources come in with different formats, it can be easily imported with right libraries. From there, data cleaning and analysis can be done easily.

